Limited information strategies for topological games

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
Add pictures to defense presentation

@@

\newcommand{\bmGame}[1]{{BM}_{E,N}(#1)}

@@

    \begin{figure}
      \includegraphics[width=0.6\linewidth]{bmGame.pdf}
    \end{figure}

@@

  This is stronger than weak
  $\alpha$-favorability, characterized by $\pl E\win\bmGame{X}$.
  In this case $\pl E$ still has a winning strategy, but it may
  rely on perfect information of the history of the game.
\end{frame}

@@

@@

\begin{frame}
  \small
  \begin{game}
  Menger's game $\menGame{X}$ proceeds as follows:

  (this space intentionally left blank until I make a picture)

>>>>

\usepackage{amssymb}

@@

\newcommand{\bmGame}[1]{{BM}_{N,E}(#1)}

@@

    \begin{figure}
      \includegraphics[width=0.6\linewidth]{bmGameAlt.pdf}
    \end{figure}

@@

  This is stronger than weak
  $\alpha$-favorability \cite{MR817083}, characterized by $\pl E\win\bmGame{X}$.
  In this case $\pl E$ still has a winning strategy, but it may
  rely on perfect information of the history of the game.
\end{frame}

@@

\begin{frame}
  For the related game $\gruConGame{X}{x}$, a $(k+1)$-tactic/mark may always
  be improved to only use the most recent move of the opponent. If this
  also holds for $\gruKPGame{X}$, then metacompactness and
  $\sigma$-metacompactness may would be characterized by the existence
  of any winning $(k+1)$-tactic/mark.

  Due to a technical difference in the games, it's unclear if this is true.
  However, for a tricky non-$\sigma$-metacompact example $\pmb X$:

  \begin{theorem}
    $\pl K\win\gruKPGame{\pmb X}$ but
    $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$.
  \end{theorem}
\end{frame}

@@

\begin{frame}
  \small
  \begin{game}
  Menger's game $\menGame{X}$ proceeds as follows:
    \begin{figure}
      \includegraphics[width=0.6\linewidth]{mengerGame.pdf}
    \end{figure}
